INTELLIGENT SYSTEMS

### 2021-04-08 paper_5.tex
working on 5.4.4

\subsubsection{Gait Recognition experiments}
\begin{enumerate}
    \item \emph{Sensor position}: 
\end{enumerate}

>>>>

\subsubsection{Gait Recognition experiments}
Different types of experiments and their respective performances, in terms of accuracy and F1-measure, are presented below.
\begin{enumerate}
    \item \emph{Sensor position}: the following experiment show that using 3 different 
    sensors, the model has greater accuracy and a high value of F1-measure, 
    when using data from the sensor positioned on the left side of the body.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
            \hline
            IMU Position & Acc & F1-score \\
            \hline
            center & 92.3 & 90.8\\
            left & \bfseries{95.2} & \bfseries{94.0}\\
            right & 91.5 & 90.0\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score of three different sensors.}
        \label{table accuracy and F1}
    \end{table}

    \item \emph{Single task with individuals sensors} (1 Task - 1 Sensor): being a multi-task 
    network, a CNN network is created for each sensor in combination 
    with each label. As there are three types of labels and two sensors, a 
    total of 6 CNN networks are trained. From the results obtained from 
    the experiment, it can be seen that both sensors affect the model in an 
    almost similar way, in terms of accuracy and F1-Measure. These values 
    indicate that both sensors can be used in order to achive the purpose 
    of identifying the walk.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                SingleTask Accelerometer & 89.7 & 91.0 & 94.8 & 91.8 & 87.6 & 91.3 & 94.5 & 91.2\\
                SingleTask Gyroscope& 89.1 & 89.1 & 94.4 & 90.9 & 87.5 & 89.7 & 94.4 & 90.5\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (1 Task - 1 Sensor).}
        \label{table accuracy and F1 (1 Task - 1 Sensor)}
    \end{table}

    \item \emph{Multi-task with individual sensors} (+ Task - 1 Sensor): in this experiment 
    more tasks are assigned to each of the sensors (3 tasks for 1 
    sensor) implying the creation of two CNN networks. This experiment 
    is useful to see if there are any performance improvements with respect 
    to the single assignment (defined in the previous point). The loss function 
    is that described in equation \ref{loss-function}. Comparing the results obtained 
    in table \ref{table accuracy and F1 (1 Task - 1 Sensor)} with table \ref{table accuracy and F1 (more Task - 1 Sensor)}, it can be seen that the following experiment led 
    to a slight improvement in performance.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||ccc|c||ccc|c|}
            \hline
                & \multicolumn{4}{c||}{Acc} & \multicolumn{4}{c|}{F1-Score} \\
            \hline
                Architecture & Id & Age & Gender & Avg & Id & Age & Gender & Avg\\
            \hline
                MultiTask Accelerometer & 90.9 & 93.3 & 95.9 & 93.4 & 89.1 & 93.3 & 95.9 & 92.8\\
                MultiTask Gyroscope & 90.1 & 90.1 & 94.8 & 91.7 & 88.3 & 90.5 & 94.9 & 91.2\\
            \hline 
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score (+ Task - 1 Sensor).}
        \label{table accuracy and F1 (more Task - 1 Sensor)}
    \end{table}

    \item \emph{Selection of the fusion position}: The fusion can take place in any convolutional 
    layer, called the common branch, of the network. For each 
    layer, a number of filters are applied which increases as the 
    depth of the network increases. As can be seen from table \ref{table accuracy and F1 fusion}, the best performances 
    are obtained in the fusion obtained in the first convolutional layer of 
    the network. Subsequent convolutional layers score lower because the 
    amount of information used for training is low.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{*{3}{|c}|}%%{|c|c|c|}
            \hline
            Position & Acc & F1-score\\
            \hline
            Conv1 & \bfseries{94.2} & \bfseries{92.9}\\
            Conv2 & 94.0 & 92.7\\
            Conv3 & 93.4 & 92.0\\
            Conv4 & 89.0 & 86.7\\
            Conv5 & 89.0 & 86.7\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Accuracy and F1-score of fusion level experiment.}
        \label{table accuracy and F1 fusion}
    \end{table}

\end{enumerate}
